### 2015-05-14 evaluation.tex
fix

We can see that \whoop reports more races than \corral. This is expected, since \whoop employs an over-approximating shared state abstraction to conservatively model the effects of additional threads when analyzing an entry point pair, and because lockset analysis is inherently imprecise; both factors can lead to false positives.  On the other hand, \corral is precise, but can miss races because only a limited number of context-switches are considered.  Another issue with \corral is loop coverage due to unsound loop unrolling. To tackle this, we enable the built-in loop over-approximation described in~\cite{lal2014powering}. This can potentially lead \corral to report false bugs, but we have not seen this in practice. Finally, when we apply \corral to a pair of entry points, we just check the specific pair and do not account for the effects of other threads (see \S\ref{corral}); this can also cause \corral to miss some races.

>>>>

We can see that \whoop reports more races than \corral does. This is because \whoop employs an over-approximating shared state abstraction to conservatively model the effects of additional threads when analyzing an entry point pair, and because lockset analysis is inherently imprecise; both factors can lead to false positives.  On the other hand, \corral is precise, but can miss races because only a limited number of context-switches are considered.  Another issue with \corral is loop coverage due to unsound loop unrolling. To tackle this, we enable the built-in loop over-approximation described in~\cite{lal2014powering}. This can potentially lead \corral to report false bugs, but we have not seen this in practice. Finally, when we apply \corral to a pair of entry points, we just check the specific pair and do not account for the effects of other threads (see \S\ref{corral}); this can also cause \corral to miss some races.
